SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-05 scipy-1.0/paper.tex
code base -> codebase
moved benchmark suite after test suite
stylization fixes

The airspeed velocity (asv\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy code base was monitored
with asv starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing (see Test suite section below), confirming 
that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our code base is improving, to empower
scientific applications.

Consider the asv benchmark results shown in Figure~\ref{fig:asvbench}, spanning
roughly nine years of project history. These demonstrate the gradual
performance improvements in a nearest-neighbor search through
\texttt{scipy.spatial.cKDTree.query()}, and can be run using:

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
\caption{Airspeed velocity benchmarks for \texttt{scipy.spatial.cKDTree.query()}
over a roughly nine year commit history time frame. The results are based on
Python 2.7 performance on the master branch of the project using NumPy 1.8.2
and Cython versions 0.27.3, 0.21.1, and 0.18 (for improved backward
compatibility). Only the L2 (Euclidean) norm is shown here, and to improve
backward compatibility and sampling of the benchmarks there was no application
of toroidal topology to the \texttt{KDTree} (boxsize argument was ignored).}
\label{fig:asvbench}
\end{figure}

Any pull request can be compared against the \texttt{master} branch with the
command \texttt{asv continuous master new-feature}. This will provide a
benchmark against the master branch and the branch a new feature is implemented
in. More features are available in the \texttt{asv} documentation\cite{asvdocs}, including 
arguments to select which benchmarks to run.

@@

>>>>

@@

The airspeed velocity (\texttt{asv}\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy code base was monitored
with \texttt{asv} starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing (see Test suite section below), confirming 
that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our code base is improving, to empower
scientific applications.

Consider the (\texttt{asv} benchmark results shown in Figure~\ref{fig:asvbench}, spanning
roughly nine years of project history. These demonstrate the gradual
performance improvements in a nearest-neighbor search through
\texttt{scipy.spatial.cKDTree.query()}, and can be run using:

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
\caption{Airspeed velocity benchmarks for \texttt{scipy.spatial.cKDTree.query}
over a roughly nine year commit history time frame. The results are based on
Python 2.7 performance on the master branch of the project using NumPy 1.8.2
and Cython versions 0.27.3, 0.21.1, and 0.18 (for improved backward
compatibility). Only the $L^2$ (Euclidean) norm is shown here, and to improve
backward compatibility and sampling of the benchmarks there was no application
of toroidal topology to the \texttt{KDTree} (boxsize argument was ignored).}
\label{fig:asvbench}
\end{figure}

Any pull request can be compared against the \texttt{master} branch with the
command \texttt{asv continuous master new-feature}. This will provide a
benchmark against the \texttt{master} branch and the branch a new feature is implemented
in. More features are available in the \texttt{asv} documentation\cite{asvdocs}, including 
arguments to select which benchmarks to run.
